\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-25 OaklandSubmission/ld.tex

To prove the correctness of our compiler, we prove that it preserves the observations in source semantics and distributed circuit semantics (see \theoremref{correctness}). 
For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the
security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
}

@@

    \inferrule*[lab={\footnotesize{E-Read}}]
               {
                 \rho \vdash x \Downarrow [\overline{c_{i}}]_{n_{1}} \\\\
                 \rho \vdash e \Downarrow n \quad n < n_{1}
               }
               {
                 \rho \vdash x[e] \Downarrow c_{n}
               }
\\\\
    \inferrule*[lab={\footnotesize{E-Arr}}]
               {
                 \forall i \in \{0 \dots n - 1\}.\:\rho \vdash e_{i} \Downarrow c_{i}
               }
               {
                 \rho \vdash [\overline{e_{i}}]_{n} \Downarrow [\overline{c_{i}}]_{n}
               }
               \hspace{0.1cm}
    \inferrule*[lab={\footnotesize{E-Inp}}]
               {
               }
               {
                 \rho \vdash \kw{in}_{j} \Downarrow c
               }
  \end{array}
  \]
  \\\\
    \fbox{$\rho \vdash s \Downarrow \rho'; O$}
  \[
  \\
  \begin{array}{c}
    \inferrule*[lab={\footnotesize{E-Decl}}]
               {
                 \rho \vdash e \Downarrow v
               }
               {
                 \rho \vdash \psi\:x = e \Downarrow \rho, x \mapsto v; \cdot
               }

@@

\subsubsection*{Source language}Our source language
(Figure~\ref{fig:srclang}) is a simple imperative language. Types
$\psi$ consist of the base types $\sigma$, and arrays
of base types $\sigma[n]$, where $n$ is the array length. Though we
model only one dimensional arrays, our implementation supports higher
dimensional arrays as well. Expressions $e$ in the language include the
integer constants $n$, \kw{bool} constants $\top$ and $\bot$,
variables $x$, binary operations $e_{1} + e_{2}$ and $e_{1} > e_{2}$,
conditionals $\cond{e}{e_{1}}{e_{2}}$, array literals 
$[\overline{e_{i}}]_{n}$\footnote{We write $\overline{e}$ (and
  similarly for other symbols) to denote a sequence of expressions.
The length of the sequence is usually clear from the context.}, and
array reads $x[e]$. The expression $\kw{in}_{j}$ denotes input from
party $j$. The statements $s$ in the language comprise of variable
declarations and assignments ($\psi\:x = e$ and $x := e$ resp.),
\kw{for} loops, array writes ($x[e_{1}] := e_{2}$), \kw{if}
statements, and sequence of statements ($s_{1}; s_{2}$). The statement
$\kw{out}\:e$ denotes revealing the value of $e$ to the
parties. The \kw{while} statement is an internal syntax that is not
exposed to the programmer.

The runtime semantics for the source language is shown in
Figure~\ref{fig:srcsem}. Values $v$, runtime environments $\rho$, and
observations $O$ are defined as follows:

@@

The judgment $\rho \vdash e \Downarrow v$ denotes the big-step
evaluation of an expression~$e$ to a value~$v$ under the runtime
environment~$\rho$. Rule ({\sc{E-Var}}) looks up the value of $x$ in
the environment. Rule ({\sc{E-Add}}) inductively evaluates $e_{1}$ and
$e_{2}$, and evaluates to their sum. Rule ({\sc{E-Read}})
evaluates an array read operation. It first evaluates $x$ to an array
value $[\overline{c_{i}}]_{n_{1}}$, and $e$ to a \kw{uint} value
$n$. It then returns $c_{n}$, the $n$-th index value in the array,
provided $n < n_{1}$, the length of the array. Rule ({\sc{E-Inp}})
evaluates to some constant $c$ denoting party $j$'s input. We model
the inputs to be base constants, an array input can be written in the
language as $[\kw{in}_{j}]_{n}$, which can then evaluate using the
rule ({\sc{E-Arr}}). The remaining rules are straightforward, and are
elided for space reasons.
\divya{Does conditionals $\cond{e}{e_{1}}{e_{2}}$ have anything interesting? just checking!}
\nc{fancy PL folks language :)}

The judgment $\rho \vdash s \Downarrow \rho_{1}; O$ represents the
big-step evaluation of a statement $s$ under environment $\rho$
producing a new environment $\rho_{1}$ and observations $O$. Rule
({\sc{E-Decl}}) evaluates the expression $e$ to $v$, and returns the
updated environment $\rho[x \mapsto v]$, with empty observations. Rule
({\sc{E-If}}) evaluates the guard expression, and then evaluates
either $s_{1}$ or $s_{2}$ accordingly. $\kw{for}$ statements evaluate
through the internal $\kw{while}$ syntax. Specifically, the rule
({\sc{E-For}}) updates $\rho$ with the initial counter value $n_{1}$,
evaluates $\loops{x}{n_{2}}{s}$ to $\rho_{1}; O$, and returns
$\rho_{1} - \{x\}$ (removing $x$ from $\rho_{1}$) and $O$. Rule
({\sc{E-LoopI}}) shows the inductive case for \kw{while}
statements, when $\rho(x) \leq n$. The rule evaluates $s$, producing
$\rho_{1}; O_{1}$. It then restricts $\rho_{1}$ to the domain of
$\rho$ ($[\rho_{1}]_{\mathsf{dom}(\rho)}$) to remove the variables
added by $s$, increments the value if $x$, and evaluates the
\kw{while} statement under this updated environment. Rule
({\sc{E-LoopT}}) is the termination case for \kw{while} statements,
when $\rho(x) > n$. Finally, the rule ({\sc{E-Out}}) evaluates the
expression, and adds its value to the observations.

@@

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Secret label} & m &::=& \mathcal{A} \mid \mathcal{B}\\
    \ftext{Label} & \ell &::=& \mathcal{P} \mid m\\
    \ftext{Type} & \tau &::=& \sigma^{\ell} \mid \sigma^{\ell}[n]\\
    \ftext{Expression} & \widetilde{e} &::=& c \mid x \mid \widetilde{e_{1}} +_{\ell} \widetilde{e_{2}} \mid \widetilde{e_{1}} >_{\ell} \widetilde{e_{2}} \\
    & & \mid & \lcond{\ell}{{\widetilde{e}}}{{\widetilde{e_{1}}}}{{\widetilde{e_{2}}}} \mid x[\widetilde{e}] \mid [\overline{\widetilde{e_{i}}}]_{n} \mid \kw{in}^{m}_{j} \mid \widetilde{e} \rhd m\\
    \ftext{Statement} & \widetilde{s} &::=& \tau\:x = \widetilde{e} \mid x := \widetilde{e} \mid \dots \mid \widetilde{s_{1}}; \widetilde{s_{2}} \mid \dots\\
  \end{array}
  \]
\caption{Target language}
\label{fig:tgtlang}
\end{figure}

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & r &&\\
    \ftext{Circuit gate} & \kappa & ::= & r \mid \kw{in}^{m}_{j} \mid \kw{add}\:\kappa_{1}\:\kappa_{2} \mid \kw{gt}\:\kappa_{1}\:\kappa_{2}\\
    & & \mid & \kw{mux}\:\kappa\:\kappa_{1}\:\kappa_{2} \mid \widetilde{w} \rhd m\\
    \ftext{Base value} & \widetilde{w} & ::= & c \mid \kappa\\
    \ftext{Value} & \widetilde{v} & ::= & \widetilde{w} \mid [\overline{\widetilde{w}_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho}[x \mapsto \widetilde{v}]\\
    \ftext{Circuit} & \chi & ::= & \cdot \mid \kw{bind}\:\kappa\:r \mid \kw{out}\:\kappa \mid \chi_{1}; \chi_{2}
  \end{array}
  \]
\caption{Target runtime}
\label{fig:tgtruntime}
\end{figure}

@@

    \inferrule*[lab={\footnotesize{S-Read}}]
               {
                 \widetilde{\rho} \vdash x \Downarrow [\overline{\widetilde{w_{i}}}]_{n_{1}} \\\\
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow n \quad n < n_{1}
               }
               {
                 \widetilde{\rho} \vdash x[\widetilde{e}] \Downarrow \widetilde{w_{n}}
               }\\\\
    \inferrule*[lab={\footnotesize{S-SAdd}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \kappa_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} +_{\mathcal{A}} \widetilde{e_{2}} \Downarrow \kw{add}\:\kappa_{1}\:\kappa_{2}
               }

@@

    \inferrule*[lab={\footnotesize{S-Inp}}]
               {
               }
               {
                 \widetilde{\rho} \vdash \kw{in}^{m}_{j} \Downarrow \kw{in}^{m}_{j}
               }
  \end{array}
  \]
  \\\\
    \fbox{$\widetilde{\rho} \vdash \widetilde{c} \Downarrow \widetilde{\rho'}; \chi$}
  \[
  \\
  \begin{array}{c}
    \inferrule*[lab={\footnotesize{S-DeclC}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \widetilde{v}\\\\
                 \widetilde{v} = c \vee \widetilde{v} = [\overline{c_{i}}]_{n}\\\\
                 \widetilde{\rho}_{1} = \widetilde{\rho}, x \mapsto \widetilde{v}
               }
               {
                 \widetilde{\rho} \vdash \tau\:x = \widetilde{e} \Downarrow \widetilde{\rho}_{1}; \cdot
               }

@@

\end{array}
  \]
\caption{Target semantics (selected rules)}
\label{fig:tgtsem}
\end{figure}

\subsubsection*{Target language} Figure~\ref{fig:tgtlang} shows the
target language of our compiler. The syntax follows that of the source
language, except that the types and operators are \emph{labeled}. Below
we mainly focus on the bits that are different from the source
language.

Most of the expression forms $\widetilde{e}$ are same as $e$, except
that the binary operators, and the conditional forms
are annotated with label $\ell$, denoting how the operators should be
evaluated ($\mathcal{P}$ for in-clear, and $\mathcal{A}$ and
$\mathcal{B}$ for using arithmetic or boolean circuits resp.). The
form $\widetilde{e} \rhd m$ denotes coercing $\widetilde{e}$ to be
$m$-secret shared. The statements $\widetilde{s}$ are analogous to
$s$.

The target semantics models the semantics of the code output by
our compiler (C++ code in our implementation). It computes over the
public parts of the program, emitting a circuit that can later be
evaluated using a cryptographic MPC protocol. The semantics also
\emph{flattens} the arrays so that the circuits are unaware of the
array structure. Crucially, this phase of the semantics does not have
access to the secrets.

Figure~\ref{fig:tgtruntime} shows the runtime syntax. A wire id range
$r$ denotes a set of circuit wires that carry the value of a secret
shared variable in the output circuit (we will concretely define these
values later as part of the circuit semantics). Circuit gates $\kappa$
are $r$, input gates, \kw{add}, \kw{gt}, and \kw{mux} gates, and
coerce gates $\widetilde{w} \rhd m$. Target values $\widetilde{v}$
then consist of base values $c$ and $\kappa$, and arrays of base
values.

Figure~\ref{fig:tgtsem} shows the judgments for the target
semantics. We first focus on the expression evaluation judgment
$\widetilde{\rho} \vdash \widetilde{e} \Downarrow
\widetilde{v}$. Rules ({\sc{S-PAdd}}) and ({\sc{S-SAdd}}) illustrate
the significance of the operator labels. In particular, the rule
({\sc{S-PAdd}}) evaluates a public addition $\widetilde{e_{1}}
+_{\mathcal{P}} \widetilde{e_{2}}$ to $n_{1} + n_{2}$, similar to the
source language. In contrast, the rule
({\sc{S-SAdd}}) evaluates a secret addition $\widetilde{e_{1}}
+_{\mathcal{A}} \widetilde{e_{2}}$ to an arithmetic add
gate $\kw{add}\:\kappa_{1}\:\kappa_{2}$. Foreshadowing on the
compilation rules to be presented later, the target
expressions from our compiler never have $\widetilde{e_{1}}
+_{\mathcal{B}} \widetilde{e_{2}}$, as our compiler is aware that $+$
is more performant using arithmetic circuit, rather than a boolean
one. Rules ({\sc{S-PCond}}) and ({\sc{S-SCond}})
are along the similar lines. Rule ({\sc{S-PCond}}) evaluates a public
conditional to the value from one of the branches, while the rule
({\sc{S-SCond}}) evaluates to a \kw{mux} gate that takes input
circuits from the conditional ($\kappa_{1}$) and both the branches
($\kappa_{2}$ and $\kappa_{3}$). Once again for performance reasons,
the target expressions from our compiler do not have
$\lcond{\mathcal{A}}{e_{1}}{e_{2}}{e_{3}}$. Rules
({\sc{S-Coerce}}) and ({\sc{S-Inp}}) evaluate to the coerce and input
gates respectively.

>>>>

To prove the correctness of our compiler, we prove that it preserves the observations in source semantics and distributed circuit semantics (see \theoremref{correctness}). 
For the security of our compiler, we rely on the correctness guarantee and  reduce the security to the
security of the underlying cryptographic protocol used to compute the generated circuit (see \theoremref{security}).
We present only selected parts of our formalization for space
reasons. \TODO{Full definitions and proofs can be found in the supplementary
material submitted along with the paper.}
}

@@

               \hspace{0.1cm}
               \inferrule*[lab={\footnotesize{E-Cond}}]
               {
                 \rho \vdash e \Downarrow c\\\\
                 c = \top \Rightarrow e' = e_{1}\\\\
                 c = \bot \Rightarrow e' = e_{2}\\\\
                 \rho \vdash e \Downarrow c'
               }
               {
                 \rho \vdash \cond{e}{e_{1}}{e_{2}} \Downarrow c'
               }

\\\\
	 \inferrule*[lab={\footnotesize{E-Read}}]
               {
                 \rho \vdash x \Downarrow [\overline{c_{i}}]_{n_{1}} \\\\
                 \rho \vdash e \Downarrow n \quad n < n_{1}
               }
               {
                 \rho \vdash x[e] \Downarrow c_{n}
               }

               \hspace{0.1cm}
    \inferrule*[lab={\footnotesize{E-Arr}}]
               {
                 \forall i \in [n].\:\rho \vdash e_{i} \Downarrow c_{i}
               }
               {
                 \rho \vdash [\overline{e_{i}}]_{n} \Downarrow [\overline{c_{i}}]_{n}
               }
               \hspace{0.1cm}
    \inferrule*[lab={\footnotesize{E-Inp}}]
               {
               }
               {
                 \rho \vdash \kw{in}_{j} \Downarrow c
               }
  \end{array}
  \]
  \\\\
    \fbox{$\rho \vdash s \Downarrow \rho'; O$}
  \[
  \\
  \begin{array}{c}
    \inferrule*[lab={\footnotesize{E-Decl}}]
               {
                 \rho \vdash e \Downarrow v
               }
               {
                 \rho \vdash \psi\:x = e \Downarrow \rho, x \mapsto v; \cdot
               }

@@

\subsubsection*{Source language}Our source language
(\figureref{srclang}) is a simple imperative language. Types
$\psi$ consist of the base types $\sigma$, and arrays
of base types $\sigma[n]$, where $n$ is the array length. Though we
model only one dimensional arrays, our implementation supports higher
dimensional arrays as well. Expressions $e$ in the language include the
integer constants $n$, \kw{bool} constants $\top$ and $\bot$,
variables $x$, binary operations $e_{1} + e_{2}$ and $e_{1} > e_{2}$,
conditionals $\cond{e}{e_{1}}{e_{2}}$, array literals 
$[\overline{e_{i}}]_{n}$\footnote{We write $\overline{e}$ (and
  similarly for other symbols) to denote a sequence of expressions.
The length of the sequence is usually clear from the context.}, and
array reads $x[e]$. The expression $\kw{in}_{j}$ denotes input from
party $j$. The statements $s$ in the language comprise of variable
declarations and assignments ($\psi\:x = e$ and $x := e$ resp.),
\kw{for} loops, array writes ($x[e_{1}] := e_{2}$), \kw{if}
statements, and sequence of statements ($s_{1}; s_{2}$). The statement
$\kw{out}\:e$ denotes revealing the value of $e$ to the
parties. The \kw{while} statement is an internal syntax that is not
exposed to the programmer.

\noindent\textbf{Source Semantics.} The runtime semantics for the source language is shown in
\figureref{srcsem}. \TODO{Add something about claer text stand alone exec.} Values $v$, runtime environments $\rho$, and
observations $O$ are defined as follows:

@@

The judgment $\rho \vdash e \Downarrow v$ denotes the big-step
evaluation of an expression~$e$ to a value~$v$ under the runtime
environment~$\rho$. Rule ({\sc{E-Var}}) looks up the value of $x$ in
the environment. Rule ({\sc{E-Add}}) inductively evaluates $e_{1}$ and
$e_{2}$, and evaluates to their sum. Rule ({\sc{E-Read}})
evaluates an array read operation. It first evaluates $x$ to an array
value $[\overline{c_{i}}]_{n_{1}}$, and $e$ to a \kw{uint} value
$n$. It then returns $c_{n}$, the $n$-th index value in the array,
provided $n < n_{1}$, the length of the array. Rule ({\sc{E-Inp}})
evaluates to some constant $c$ denoting party $j$'s input. We model
the inputs to be base constants, an array input can be written in the
language as $[\kw{in}_{j}]_{n}$, which can then evaluate using the
rule ({\sc{E-Arr}}). The remaining rules are straightforward, and are
elided for space reasons.

The judgment $\rho \vdash s \Downarrow \rho_{1}; O$ represents the
big-step evaluation of a statement $s$ under environment $\rho$
producing a new environment $\rho_{1}$ and observations $O$. Rule
({\sc{E-Decl}}) evaluates the expression $e$ to $v$, and returns the
updated environment $\rho,x \mapsto v$, with empty observations. Rule
({\sc{E-If}}) evaluates the guard expression, and then evaluates
either $s_{1}$ or $s_{2}$ accordingly. The $\kw{for}$ statements evaluate
through the internal $\kw{while}$ syntax. Specifically, the rule
({\sc{E-For}}) appends $\rho$ with $x\mapsto n_{1}$,
evaluates $\loops{x}{n_{2}}{s}$ to $\rho_{1}; O$, and returns
$\rho_{1} - \{x\}$ (removing $x$ from $\rho_{1}$) and $O$. Rule
({\sc{E-LoopI}}) shows the inductive case for \kw{while}
statements, when $\rho(x) \leq n$. The rule evaluates $s$, producing
$\rho_{1}; O_{1}$. It then restricts $\rho_{1}$ to the domain of
$\rho$ ($[\rho_{1}]_{\mathsf{dom}(\rho)}$) to remove the variables
added by $s$, increments the value of $x$, and evaluates the
\kw{while} statement under this updated environment. Rule
({\sc{E-LoopT}}) is the termination case for \kw{while} statements,
when $\rho(x) > n$. Finally, the rule ({\sc{E-Out}}) evaluates the
expression, and adds its value to the observations.

@@

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Secret label} & m &::=& \mathcal{A} \mid \mathcal{B}\\
    \ftext{Label} & \ell &::=& \mathcal{P} \mid m\\
    \ftext{Type} & \tau &::=& \sigma^{\ell} \mid \sigma^{\ell}[n]\\
    \ftext{Expression} & \widetilde{e} &::=& c \mid x \mid \widetilde{e_{1}} +_{\ell} \widetilde{e_{2}} \mid \widetilde{e_{1}} >_{\ell} \widetilde{e_{2}} \\
    & & \mid & \lcond{\ell}{{\widetilde{e}}}{{\widetilde{e_{1}}}}{{\widetilde{e_{2}}}} \mid x[\widetilde{e}] \mid [\overline{\widetilde{e_{i}}}]_{n} \mid \kw{in}^{m}_{j} \mid \widetilde{e} \rhd m\\
    \ftext{Statement} & \widetilde{s} &::=& \tau\:x = \widetilde{e} \mid x := \widetilde{e} \mid \dots \mid \widetilde{s_{1}}; \widetilde{s_{2}} \mid \dots\\
  \end{array}
  \]
\caption{Intermediate Language}
\label{fig:interlang}
\end{figure}

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & \wire &&\\
    \ftext{Circuit gate} & \gate & ::= & \wire \mid \kw{in}^{m}_{j} \mid \kw{add}\:\gate_1\:\gate_{2} \mid \kw{gt}\:\gate_{1}\:\gate_{2}\\
    & & \mid & \kw{mux}\:\gate\:\gate_{1}\:\gate_{2} \mid \widetilde{w} \rhd m\\
    \ftext{Base value} & \bval & ::= & c \mid \gate\\
    \ftext{Value} & \val & ::= & \bval \mid [\overline{\bval_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho},x \mapsto \val \\
    \ftext{Circuit} & \crct & ::= & \cdot \mid \kw{bind}\:\gate\:\wire \mid \kw{out}\:\gate \mid \crct_{1}; \crct_{2}
  \end{array}
  \]
\caption{Circuits   \divya{Is environ misplaced?}}
\label{fig:circuits}
\end{figure}

\subsubsection*{Intermediate language} \figureref{interlang} shows the
intermediate language of our compiler. The syntax follows that of the source
language, except that the types and operators are \emph{labeled}. Below
we mainly focus on the bits that are different from the source
language.

Most of the expression forms $\widetilde{e}$ are same as $e$, except
that the binary operators, and the conditional forms
are annotated with label $\ell$, denoting how the operators should be
evaluated ($\mathcal{P}$ for in-clear, and $\mathcal{A}$ and
$\mathcal{B}$ for using arithmetic or boolean circuits resp.). The
form $\widetilde{e} \rhd m$ denotes coercing \divya{the value of} $\widetilde{e}$ to be
$m$-secret shared. The statements $\widetilde{s}$ are analogous to
$s$.

\aseem{The target semantics models the semantics of the code output by
our compiler (C++ code in our implementation).}
A program in the intermediate language is evaluated to a circuit that can be executed in the distributed setting later. The evaluation to a circuit computes over the public parts of the program and also \emph{flattens} the arrays so that the circuits are unaware of the array structure. 
Crucially, this phase of the semantics does not have access to the secrets.
Below, we first provide the language for the circuits used followed by our evaluation rules.

\subsubsection*{Circuits}
\figureref{circuits} shows the circuits syntax. A wire id range
$\wire$ denotes a set of circuit wires that carry the value of a secret
shared variable in the output circuit (we will concretely define these
values later as part of the circuit semantics). Circuit gates $\gate$
are $\wire$, input gates, \kw{add}, \kw{gt}, and \kw{mux} gates, and
coerce gates $\bval \rhd m$. \divya{Gates are not just gates but a circuit?} Target values $\val$
then consist of base values $c$ and $\gate$, and arrays of base
values. \\

\divya{Start here....}
\noindent\textbf{Evaluation to Circuit.} \figureref{eval-inter-circ} shows the judgments for the evaluation of the intermediate language to a circuit. We first focus on the expression evaluation judgment
$\widetilde{\rho} \vdash \widetilde{e} \Downarrow
\val$. 
%
Rules ({\sc{S-PAdd}}) and ({\sc{S-SAdd}}) illustrate
the significance of the operator labels. In particular, the rule
({\sc{S-PAdd}}) evaluates a public addition $\widetilde{e_{1}}
+_{\mathcal{P}} \widetilde{e_{2}}$ to $n_{1} + n_{2}$, similar to the
source language. In contrast, the rule
({\sc{S-SAdd}}) evaluates a secret addition $\widetilde{e_{1}}
+_{\mathcal{A}} \widetilde{e_{2}}$ to an arithmetic add
gate $\kw{add}\:\kappa_{1}\:\kappa_{2}$. Foreshadowing on the
compilation rules to be presented later, the target
expressions from our compiler never have $\widetilde{e_{1}}
+_{\mathcal{B}} \widetilde{e_{2}}$, as our compiler is aware that $+$
is more performant using arithmetic circuit, rather than a boolean
one. Rules ({\sc{S-PCond}}) and ({\sc{S-SCond}})
are along the similar lines. Rule ({\sc{S-PCond}}) evaluates a public
conditional to the value from one of the branches, while the rule
({\sc{S-SCond}}) evaluates to a \kw{mux} gate that takes input
circuits from the conditional ($\kappa_{1}$) and both the branches
($\kappa_{2}$ and $\kappa_{3}$). Once again for performance reasons,
the target expressions from our compiler do not have
$\lcond{\mathcal{A}}{e_{1}}{e_{2}}{e_{3}}$. Rules
({\sc{S-Coerce}}) and ({\sc{S-Inp}}) evaluate to the coerce and input
gates respectively.

@@

    \inferrule*[lab={\footnotesize{S-Read}}]
               {
                 \widetilde{\rho} \vdash x \Downarrow [\overline{\bval_i}]_{n_{1}} \\\\
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow n \quad n < n_{1}
               }
               {
                 \widetilde{\rho} \vdash x[\widetilde{e}] \Downarrow \bval_n
               }\\\\
    \inferrule*[lab={\footnotesize{S-SAdd}}]
               {
                 \forall i \in \{1, 2\}.\:\widetilde{\rho} \vdash \widetilde{e_{i}} \Downarrow \kappa_{i}
               }
               {
                 \widetilde{\rho} \vdash \widetilde{e_{1}} +_{\mathcal{A}} \widetilde{e_{2}} \Downarrow \kw{add}\:\kappa_{1}\:\kappa_{2}
               }

@@

    \inferrule*[lab={\footnotesize{S-Inp}}]
               {
               }
               {
                 \widetilde{\rho} \vdash \kw{in}^{m}_{j} \Downarrow \kw{in}^{m}_{j}
               }
  \end{array}
  \]
  \\\\
    \fbox{$\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho'}; \chi$}
  \[
  \\
  \begin{array}{c}
    \inferrule*[lab={\footnotesize{S-DeclC}}]
               {
                 \widetilde{\rho} \vdash \widetilde{e} \Downarrow \widetilde{v}\\\\
                 \widetilde{v} = c \vee \widetilde{v} = [\overline{c_{i}}]_{n}\\\\
                 \widetilde{\rho}_{1} = \widetilde{\rho}, x \mapsto \widetilde{v}
               }
               {
                 \widetilde{\rho} \vdash \tau\:x = \widetilde{e} \Downarrow \widetilde{\rho}_{1}; \cdot
               }

@@

\end{array}
  \]
\caption{Evaluation of Intermediate Language to Circuit (selected rules)}
\label{fig:eval-inter-circ}
\end{figure}
